---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# centralisedapproach

<!-- badges: start -->
<!-- badges: end -->

The goal of centralisedapproach is to provide the tools to produce distributional household wealth estimates in line with the OECD centralised approach. It also allows to generate figures to visualize the main results. 

## Installation

You can install the development version of centralisedapproach from [GitHub](https://github.com/) with:

``` {r installation, message = FALSE}
# install.packages("devtools") #install devtools if not installed
library(devtools)
devtools::install_github("elenasolaveranavarro/EGDHW")
```

## Step 1: importing national accounts data

This is a basic example which shows you how to load the macro totals from OECD data explorer for a given country and year. 

```{r example}
library(centralisedapproach)

## Define the country for the analysis (ISO-2, lowercase, for Luxembourg Wealth Study)
country <- "ESP"

## Set the year for analysis. This will be the year for the national accounts and either the year or interpolated year for the survey
year <- 2022

# Working directory
# setwd("...")

# # Use the egdhwNationalAccountsTotals to retrieve the macro data
# var_name <- paste0(country,"_",year) 
# assign(var_name, egdhwNationalAccountsTotals(country,"S1M", year, consolidated = FALSE))
# 
# # Merge predefined dataframe to have all the relevant variable/code pairs
# nationalAccounts <- nationalAccounts %>%
#   left_join(get(paste0(country,"_",year)), by = c("codes" = "series"), copy = TRUE) %>%  
#   mutate(values = OBS_VALUE) %>%
#   select(name, codes, values)

```

## Step 2: compute distributional estimates in LISSY

Access to the LWS microdata is only granted in the online server LISSY. As such, the script to generate distributional household estimates needs to be run in LISSY.

Note that we perform certain adjustments to better capture the wealth distribution. Since the wealthiest households tend to be underrepresented in survey data, we use a selectivity correction model to account for this missing households in the micro totals. For more details, see ParetoGrilli (need to insert link)

```{r match}
#matching()
```

You'll still need to render `README.Rmd` regularly, to keep `README.md` up-to-date. `devtools::build_readme()` is handy for this.

## Step 3: Visualization

```{r pressure, echo = FALSE}
plot(pressure)
# If you include figures or graphs, don't forget to commit and push the resulting figure files, so they display on GitHub and CRAN.
```


